Sparse Representation Approaches for First Stage Retrieval: A Review

### 2021-12-03 src/article.tex
Update section [Sparse representation]

    Sparse retrieval methods usually represent each document and each query with sparse vectors,
    where only a small number of dimensions are active.
    The sparse representation has attracted great attention as it connects to the nature of human
    memories and shows better interpretability.

    Besides, sparse representations can be easily integrated into existing inverted indexing
    engines for efficient retrieval.

>>>>

    Sparse retrieval methods usually represent each document and each query with sparse vectors,
    where only a small number of dimensions are active.
    The sparse representation has attracted great attention as it connects to the nature of human
    memories and shows better interpretability.
    Since usually the term is replaced with a numeric value and has a one-to-one correspondence
    in the vocabulary of words.
    This feature makes it easy to use sparse representations on an inverted index, in this case
    each value of the term map to the document in which it occurs.

    During the search, the query is broken down into terms in the same way as documents, then
    they are used as keys in the inverted index to find the corresponding documents.
    The more query terms are found in a document, the more suitable it is for re-ranking.
